---
output:
  word_document: default
  html_document: default
  pdf_document: default
---
## **Part 1 - Import NVIDIA stock data using quantmod and visualize the closing prices over time.**

### **Load necessary packages**

```{r, message=FALSE, warning=FALSE}
library(quantmod)
```

### **Importing NVIDIA stock data using quantmod**

```{r}
getSymbols("NVDA", src = "yahoo", from = "2023-04-01", to = "2024-04-01")
```

### **Visualization of NVIDIA's Gains & Losses over a period of 1 year**

#### **Green = gains; Red = losses**

```{r}
chartSeries(NVDA, theme = chartTheme("white"))
```

## **Part 2 - Calculate daily and monthly returns for NVIDIA and Create plots showing price trends and returns.**

### **Calculate daily returns using the quantmod package with the function dailyReturn().**

#### **This function computes the percentage change between the closing prices of two consecutive days (y axis = rate of change).**

```{r}
NVDA_daily_returns <- dailyReturn(NVDA)
```

### **Calculate monthly returns using the quantmad package.**

#### **Involves converting daily stock prices to monthly prices and then computing the returns based on these monthly prices.**

```{r}
NVDA_monthly_returns <- monthlyReturn(NVDA)
```

### **Visualizing daily returns of NVDA**

```{r}
barChart(NVDA_daily_returns, theme = chartTheme("black", grid.col="gray"), name =  "Daily Returns for NVDA")
```

### **Visualizing monthly returns of NVDA**

```{r}
barChart(NVDA_monthly_returns, theme = chartTheme("white"), name = "Monthly Returns for NVDA")
```

## **Part 3 - Compute and plot moving averages and volatility for NVIDIA and Apply technical indicators to generate trading signals.**

### **Moving averages**

#### **SMA calculates the arithmetic mean of the series over the past n observations.**

#### **Enhanced chart with volume and SMA overlays**

#### **Visualization with SMA = 20**

```{r}
chartSeries(NVDA, TA = "addVo();addSMA(20)",theme = chartTheme("white"))
```

#### **Visualization with SMA = 50**

```{r}
chartSeries(NVDA, TA = "addVo();addSMA(50)",theme = chartTheme("white"))
```

### **Volatility (standard deviation of daily returns)**

#### **Volatility is a statistical measure of the dispersion of returns for a given security or market index, and it's typically used to quantify the risk associated with a particular investment.**

```{r}
NVDA_volatility <- runSD(NVDA_daily_returns, n = 20)
```

#### **Plotting volatility**

```{r}
plot(NVDA_volatility, main = "20-Day Rolling Volatility of NVDA")
```

### **Technical indicators**

#### **Moving Average Convergence/Divergence (MACD)**

##### **Relative Strength Index (RSI) calculates a ratio of the recent upward price movements to the absolute price movement.**

```{r}
NVDA_macd_vals <- MACD(Cl(NVDA))
NVDA_rsi_vals <- RSI(Cl(NVDA))
```

#### **Plotting MACD of NVDA**

```{r}
plot(NVDA_macd_vals, main = "MACD NVDA")
```

#### **Plotting RSI of NVDA**

```{r}
plot(NVDA_rsi_vals, main = "RSI NVDA")
```

#### **Plotting with technical indicators**

```{r}
chartSeries(NVDA, TA = "addVo();addMACD();addRSI();addSMA(20);addVolatility()",theme = chartTheme("white"))
```

## **Part 4 - Build a simple ARIMA model to forecast next month's prices for NVIDIA and Evaluate the model’s accuracy and discuss its implications.**

### **Load necessary libraries**

```{r, message=FALSE, warning=FALSE}
library(forecast)
```

### **Visualization without forecasting**

```{r}
plot(NVDA$NVDA.Open, main = "NVDA Open Price without forecasting")
```

### **Fit an ARIMA model**

```{r}
NVDA_OPfit <- auto.arima(NVDA$NVDA.Open)
```

### **Model parameters**

```{r}
summary(NVDA_OPfit)
```

##### **ARIMA(0,1,1)**

##### **We have an ARIMA model: ARIMA(0,1,1)**

##### **0 for the AR (autoregressive) part, indicating no lagged term of the variable was used.**

##### **1 for the I (integrated) part, meaning the data has been differenced once to achieve stationarity.**

##### **1 for the MA (moving average) part, indicating that the model uses one lagged forecast error term.**

### **Check model diagnostics**

```{r, message=FALSE, warning=FALSE}
checkresiduals(NVDA_OPfit)
```

### **Create a forecast**

```{r}
NVDA_OP_future_values <- forecast(NVDA_OPfit, 20)  # Forecasting next 20 values
```

### **Plot the forecast with historical data, showing 80% & 95% prediction intervals obtained using exponential smoothing state space models**

```{r}
plot(NVDA_OP_future_values, main = "NVDA Open Price with forecasting")
```

## **Interpretation:**

### ***As we look at the forecast, we see that the trend is upward, indicating that the model predicts continued growth in NVIDIA’s stock price. It’s not a flat line, which would suggest uncertainty or no clear trend.***

### ***In this current forecast, the model is confident enough to predict an upward trend. This is shown within the 80% confidence interval, suggesting that while we are fairly certain about the growth, there is still a 20% chance that the actual prices could fall outside this range. The prices are expected to grow, but they could fluctuate within the values outlined by this interval.***

### ***On the other hand, the 95% confidence interval is wider, accounting for more variability. It implies that while the overall trend suggests little change, the stock price could experience significant volatility within this interval. Essentially, 95% of the time, the price could swing wildly up or down but ultimately lead to a relatively stable trend over the forecast period.***
